---
title: "Homework: Reproducibility and Professional Communication"
execute:
  error: true
author: "Kaitlyn Steck"
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits = 3)
```


# Reproducible Examples & Debugging

In the following examples, evaluate each problem using the criteria of a minimal reproducible example from [this StackOverflow post](https://stackoverflow.com/help/minimal-reproducible-example). 

Specifically, address the following things: 

1. Are the question and problem description complete?

2. Is the issue reproducible? Does it have a description of the problem, with code that reproduces the problem? What could improve it?

3. Is the example minimal? Does it include extra code or information that is not necessary?

4. Does the question describe any attempted solutions?


Then, using what you know about R and Python, try to debug the problem using the strategies in [the debugging chapter](https://srvanderplas.github.io/stat-computing-r-python/part-gen-prog/06-debugging.html). Once you are thoroughly stumped, or you believe you have solved the problem, compare your solutions to those given on StackOverflow using the link.

## Why Doesn't this R function work?

> I created the following function to append new strings on a vector of strings called "meals". However, when I use this function to append an string input into my "meals" vector, it does not work.

```
 add <- function(str) {
      meals <- append(meals, as.character(str))  
    }
```

[Link](https://stackoverflow.com/questions/39795961/why-doesnt-this-r-function-work?noredirect=1&lq=1) to original SO post. 

```{R}

## Debugging attempt from stackoverflow

meals<- c("steak", "pasta")

 add <- function(str) {
      meals <<- append(meals, as.character(str))  
 }
 
add("soup")
meals
```

---

1. Are the question and problem description complete?

> <!--No, I am not completely sure what they are attempting to do with the new function. There is not enough information about what is in the vectors or what they are attempting to do with 'str'. -->  

2. Is the issue reproducible? Does it have a description of the problem, with code that reproduces the problem? What could improve it?

> <!--There is little description of the problem, only that "it does not work." The author also does not provide reproducible code. They should be providing code with a built in data set so that others can replicate the issue. They should also provide more information about what they are attempting to do with the function. -->

3. Is the example minimal? Does it include extra code or information that is not necessary?

> <!--The example is minimal, but too minimal. There is not enough information provided to help troubleshoot the issue. -->

4. Does the question describe any attempted solutions?

> <!--No, they do not describe any attempted solutions. -->


## Function not working R

> I've never programmed before and am trying to learn. I'm following that "coursera" course that I've seen other people post about ??? a course offered by Johns Hopkins on R programming.

> Anyway, this was supposed to be my first function. Yet, it doesn't work! But when I type out all the steps individually, it runs just fine... Can anyone tell me why?

```
pollutantmean <- function(directory, pollutant, id = 1:332){
    x<- list.files("/Users/mike******/Desktop/directory", full.names=TRUE)
    y<- lapply(x, read.csv)
    z<- do.call(rbind.data.frame, y[id])

    mean(z$pollutant, na.rm=TRUE)
}
pollutantmean(specdata,nitrate,1:10)
[1] NA
Warning message:
In mean.default(z$pollutant, na.rm = TRUE) :
  argument is not numeric or logical: returning NA

####

x<- list.files("/Users/mike******/Desktop/specdata",full.names=TRUE)
y<- lapply(x,read.csv)
z<- do.call(rbind.data.frame,y[1:10])
mean(z$nitrate,na.rm=TRUE)
[1] 0.7976266
```


[Link](https://stackoverflow.com/questions/24123224/function-not-working-r/24141502)

```{R}

## First, the step by step code they provide is not the same as the function they created. For example, mean(z$pollutant) vs mean(z$nitrate) so they are calling variables different names throughout. 

pollutantmean <- function(specdata, pollutant, id = 1:332){
    specdata<- list.files("/Users/mike******/Desktop/specdata", full.names=TRUE) ### I think "directory should be "specdata" so it needs to be called instead of directory
    y<- lapply(specdata, read.csv)
    z<- do.call(rbind.data.frame, y[id])

    mean(z$pollutant, na.rm=TRUE)
}
pollutantmean(specdata,nitrate,1:10)
[1] NA


```
---

1. Are the question and problem description complete?

> <!--No, we do not have the full context of the problem they are trying to complete. I do not know what they are attempting to do with their code.--> 

2. Is the issue reproducible? Does it have a description of the problem, with code that reproduces the problem? What could improve it?

> <!--We can see the issue in their code, but the code itself is not reproducible based on the information we are given. Some of the data is in their directory which we cannot access. A built in dataset with the issue would allow us to reproduce the issue.  -->

3. Is the example minimal? Does it include extra code or information that is not necessary?

> <!--Yes, they gave enough information about the data. There was not extra information that is not necessary. -->

4. Does the question describe any attempted solutions?

> <!--No, they do not describe any attempted solutions. They do show the error message that is produced and that each line will run on its own, but not attempted solutions. -->


## Inexplicable error when trying to export my R notebook

> Getting this error from R Markdown when trying to export my .RMD

```
"Error in filter(Gastropods, Species == "Cellana") :  object 'Species' not found Calls: <Anonymous> ... withCallingHandlers -> withVisible -> eval -> eval -> filter"
```

> However, all my plots are coming out successfully. I can clearly see in the data that the species column is there and that Cellana is a species. No spelling errors or anything.

> My first 20 or so lines of code are below (between the ### symbols)


````{r echo=FALSE}
cat(paste(readLines("https://raw.githubusercontent.com/unl-statistics/stat850/refs/heads/main/homework/debugging_3.txt"), collapse = '\n'))
````

You can find this sample file [here](https://raw.githubusercontent.com/unl-statistics/stat850/refs/heads/main/homework/debugging_3.txt)


[Link](https://stackoverflow.com/questions/44193367/inexplicable-error-when-trying-to-export-my-r-notebook)

The issue is coming from library(ggplot2, dplyr) as you cannot load those two packages together. The person is likely assuming "dplyr" is loaded and is trying to use "filter" which is a "dplyr" function. 

---

1. Are the question and problem description complete?

> <!--Yes, the question and problem description is complete. -->

2. Is the issue reproducible? Does it have a description of the problem, with code that reproduces the problem? What could improve it?

> <!-- This not reproducible because we do not have a dataset for us to attempt to replicate the issue. There is a description of the problem and clear code that is being used, which is extremely helpful. They could provide the issue with a public dataset so others could attempt to reproduce the issue. -->

3. Is the example minimal? Does it include extra code or information that is not necessary?

> <!-- The example is minimal, there is not extra information that is not necessary.-->

4. Does the question describe any attempted solutions?

> <!-- Yes, they acknowledge they checked for spelling errors and column names. -->


## Python if elif else statement

> I'm trying to create a program with python that calculate the cost for shipping.

> However, I can't run the program to where it works properly.

> What ever my total is the same amount comes out as $6 for US and $8 for Canada. I can't seem to get pass that.

> Example:

```
total = raw_input('What is the total amount for your online shopping?')
country = raw_input('Shipping within the US or Canada?')

if country == "US":
    if total <= "50":
        print "Shipping Costs $6.00"
    elif total <= "100":
            print "Shipping Costs $9.00"
    elif total <= "150":
            print "Shipping Costs $12.00"
    else:
        print "FREE"

if country == "Canada":
    if total <= "50":
        print "Shipping Costs $8.00"
    elif total <= "100":
        print "Shipping Costs $12.00"
    elif total <= "150":
        print "Shipping Costs $15.00"
    else:
        print "FREE"
```


[Link](https://stackoverflow.com/questions/19371643/python-if-elif-else-statement)

They need to remove the quotation marks from the price before the print, for example "50": should be 50: as it is not being read as an integer. Also, when looking at stackoverflow, someone pointed out that the "total = raw_input('What is the total amount for your online shopping?')" should have "total = int(raw...)" at the begining. 

---

1. Are the question and problem description complete?

> <!-- Yes, the question and problem description is complete. -->

2. Is the issue reproducible? Does it have a description of the problem, with code that reproduces the problem? What could improve it?

> <!-- It is not reproducible because we cannot work with the data, they should provide code that people can work with on their computer. While there is a description of the problem, we cannot reproduce it because we do not have the dataset. Thus, a built in dataset could improve the question. -->

3. Is the example minimal? Does it include extra code or information that is not necessary?

> <!-- The example is minimal and does not include extra code or information that is not necessary. -->

4. Does the question describe any attempted solutions?

> <!-- They do not describe any attempted solutions -->


# Professional Communication

## Slides

Create a set of quarto slides in the file slides.qmd. 

Set two different output formats - for instance, reveal.js and beamer. 

In your slides:

- Introduce yourself and show a picture of yourself
- Provide basic biographical information: birthday, where you grew up
- Show a picture of your favorite animal
- Provide your favorite plot, generated in either R or python. (This can be one you've generated in this class). Ensure that the code does not show, but the plot does.
- Provide a link to your CV, which you will generate in the next part.

## CV

Select a CV template that uses either LaTeX or Markdown:

- https://github.com/kazuyanagimoto/quarto-awesomecv-typst
- https://github.com/schochastics/quarto-cv
- https://www.overleaf.com/latex/templates/tagged/cv

Use the template to create a curriculum vitae that has your education, work experience, and any other sections you would like to include. Compile your CV and link to it in your slides. 
